\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ledjo Lleshaj} \\ \vspace{1pt}
    \small (+39) 388-244-1632 $|$ \href{mailto:ledjolleshaj@yahoo.com}{\underline{ledjolleshaj@yahoo.com}} $|$ 
    \href{https://linkedin.com/in/ledjo-lleshaj/}{\underline{linkedin.com/in/ledjo-lleshaj/}} $|$
    \href{https://github.com/LedjoLleshaj}{\underline{github.com/ledjolleshaj}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {University of Verona}{Verona, Italy}
      {Master in Computer Science and Engineering}{Oct. 2022 -- Oct 2025}

      \textbf{Thesis:} \emph{Using LLMs to Translate Natural
Language into SQL Queries}
    \resumeSubheading
      {University of Verona}{Verona, Italy}
      {Bachelor in Computer Science}{Oct. 2019 -- Oct 2022}

      \textbf{Thesis:} \emph{Frontend about a fitbit health check and suggestion system, based on Apriori Algorithm using Ionic Vue framework.}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IT Support Specialist}{Sept 2024 -- Oct 2025}
      {Generali Italia: Banca e Assicurazioni}{Verona, Italy}
      \resumeItemListStart
        \resumeItem{Provided technical assistance to employees by troubleshooting hardware, software, and network issues, ensuring minimal downtime and smooth daily operations.}
      \resumeItemListEnd
      

    \resumeSubheading
      {SOFTWARE DEVELOPER - INTERNSHIP}{Jan. 2024 -- May 2024}
      {BSQ Security}{Verona, Italy}
      \resumeItemListStart
        \resumeItem{Debugged and tested the web application qboard.app using pytest.}
        \resumeItem{Developed a Flask-based backend server for an alarm system featuring AI-powered CCTV detection.}
        \resumeItem{Built a Telegram bot to deliver automated alarm notifications to subscribed users, integrating with the backend system.}
        \resumeItem{Conducted comprehensive testing and authored technical documentation to ensure reliability and maintainability.}
    \resumeItemListEnd

    \resumeSubheading
      {VUE DEVELOPER - INTERNSHIP}{Dec 2022 -- April 2023}
      {RealT}{Verona, Italy}
      \resumeItemListStart
        \resumeItem{Developed an application using Vue, TypeScript, Tailwind CSS, and Docker.}

      \resumeItemListEnd
    \resumeSubheading
      {CYBERCHALLENGE}{Feb 2022 -- Jun 2022}
      {\href{https://cyberchallenge.it/}{\underline{Cyberchallenge.it}}}{University of Verona, Italy}
      \resumeItemListStart
        \resumeItem{After passing the selection test i attended a 4-month training program on Cybersecurity covering topics such as Network Security, Web Application Security, Cryptography, and Ethical Hacking.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Personal Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Store inventory managment system} $|$ \emph{Python, Django, Angular, PostgreSQL, Docker}}{March 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application using Django in backend with databse in PostgreSQL and Angular for the Frontend to manage the inventory/sales/restock for a fish store}
            \resumeItem{Deployed and hosted the application using Docker containers which is currently in use by the store owner}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hospitium} $|$ \emph{School Project done in Java SpringBoot, Gradle, Git, H2 database}}{}
          \resumeItemListStart
            \resumeItem{Developed a software system to manage the operations of a medical clinic.}
            \resumeItem{Supported multiple doctors and nurses in handling medications and blood test workflows.}
            \resumeItem{Implemented features for a shared secretarial office to manage appointments and patient records.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Vue-job-search} $|$ \emph{School Project done in Typescript using Vue, Rest Api, PostgreSQL database, and django in Git}}{}
          \resumeItemListStart
            \resumeItem{Developed a software system to help users search for jobs based on various criteria such as location, job type, and keywords.}
            \resumeItem{Implemented user authentication and profile management features.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Java, Python, C, SQL (Postgres), JavaScript, Typescript} \\
     \textbf{Frameworks}{: Spring Boot, Django, Flask, Node.js, JUnit, Angular, FastAPI, TailwindCss} \\
     \textbf{Developer Tools}{: Git, Docker, VS-Code, IntelliJ, Linux, Postman} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Transformers, PyTorch, Scikit-learn} \\
     \textbf{Languages}{: Albanian (Native), English (Fluent) C1-C2, Italian (Fluent) C1-C2}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
